Combinatorial Identities from Lagrange's Interpolation Polynomial

### 2020-11-04 spectral radius of matrix new method/thesis/article110320.tex
1104 temp saved

\documentclass{article}
% \topmargin 0pt

@@

@@

\section{Our Method}
We use [n-1] as notation of the set of elements from one to n-1, which is {1,2,$...$,n}.
Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the position $k,n$ of $E_{kn}$. We will apply the previous theorem with $P=I$ and $$Q=I+E_{kn}=\begin{pmatrix}
1 &  & & &  & 0 \\
 & 1 &  &      &  &  \\
 &  & \ddots & &  & 1 \\
 &  &        & &  &  \\
  &  & & & 1 &  \\
0 &  & & &  & 1 \\
\end{pmatrix}.$$

% 
    { $k$-rooted vector}

\begin{defn}
 A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
\end{defn}
\bigskip

@@

\begin{lem}
\begin{equation}
    \textit{vector rooted lemma}\label{v_rooted}
\end{equation}
If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
\begin{enumerate}
\item[(i)] $v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
\item[(ii)] $u_k>0$ if and only if $v'_k>v'_n$.
\end{enumerate}
\qed
\end{lem}

% 
    { Our first result}

\begin{thm}\label{thm_main}
    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}
\item[(i)]   $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
\item[(ii)] there exist a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
\item[(iii)] there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
\item[(iv)] $v^Tv'>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{enumerate}
\item[(a)] $c_{ik}+c_{in}=c'_{ik}+c'_{in}$\qquad for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
\item[(b)]
$c'_{ij}=c_{ij}\qquad \hbox{for~}1\leq i\leq n,~1\leq j\leq n-1 \hbox{~with~} v_i\ne 0 \hbox{~and~} v'_j> v'_n.$
\end{enumerate} \qed
\end{thm}
%

@@

% 
    {\bf $k$-rooted matrix}
    \begin{defn}[(k,n)-sum]
        For a matrix $C'=(c'_{ij})$ of $n$ columns, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
    \end{defn}

@@

    { Proof}

The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by (~\ref{v_rooted}), For certain d, if C'+dI is k-rooted, then it has a k-rooted eigenvector with its spectral radius $\lambda + d$. C' would share the same eigenvector with C'+dI and has eigenvalue $\lambda$. So C'+dI and C+dI meet the conditions of (\ref{l_diag}), and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and then $\rho(C') \geq \rho(C)$  \qed

    { Example}
    For the following $4\times 4$ matrix
    $$C=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 0 & 1\\
    1 & 1 & 0 & 1\\
    1 & 1 & 1 & 0
    \end{pmatrix},$$
    we choose
    $$C'=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 1 &  0\\
    1 & 1 & 0 & 1\\
    1 & 1 & 1 & 0
    \end{pmatrix}.$$
    Then
    $\rho(C)\leq \rho(C')$ by previous theorem.

    {Counterexample}
    For the following two $4\times 4$ matrices
    $$C=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 0 & 1\\
    1 & 1 & 0 & 0\\
    1 & 1 & 1 & 0
    \end{pmatrix},\quad C'=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 1 &  0\\
    1 & 1 & 0 & 0\\
    1 & 1 & 1 & 0
    \end{pmatrix},$$ 
    we have $CQ\leq C'Q$, but 
    $\rho(C)=2.234\not\leq 2.148= \rho(C')$. 
    This is because $c'_{33}+c'_{34}\not\geq c'_{43}+c'_{44}$.

>>>>

\documentclass{article}

% \topmargin 0pt

@@

%\renewcommand {\refname} {Bibliography}

@@

\section{Preliminaries}

    Let $\mathbb{R}$ and $\mathbb{C}$ denote the

field of real numbers and complex numbers respectively.
    \begin{defn}

Let $C$ be an $n \times n$ real nonnegative matrix, and $u \in \mathbb{R}^n$ be a

nonzero column vector. The scalar $\lambda \in \mathbb{C}$ is an $\it{eigenvalue}$

of C corresponding to the $\it{eigenvector}$ $u,$  if $Cu = \lambda u.$

%Also, $C$ has an left eigenvector $v^T$, when $v^TC=\lambda v^T$.
    \end{defn}

   \begin{defn}
        When $C$ is an $n \times n$ real matrix, the $\textit

{spectral radius} $ $\rho(C)$ of $C$ is defined by
        $$\rho(C):=\max\{~|

\lambda|~\ |~~\lambda\hbox{ is an eigenvalue of $C$}\},$$
        where $|

\lambda|$ is the magnitude of complex number $\lambda.$
    \end{defn}

\begin{thm} 
        %\bf{Perron–Frobenius theorem} \\
        If $C$ is

nonnegative square matrix, then the spectral radius $\rho(C)$ is an eigenvalue of

$C$ with a corresponding nonnogative right eigenvector and a corresponding

nonnegative left eigenvector.
    \end{thm}

    We are interested in spectral

radius of the following matrix associated with a simple graph.

    \begin{defn}

  Given an undirected graph G, the$\textit{ adjacency matrix}$ of G is the square

matrix $A = (a_{ij})$ indexed by vertices of G, and
    \[a_{ij} =\begin{cases}

 1, \text{if $i$ is adjacent to $j$}, \\
    0, \text{otherwise.}
    \end{cases}

   \]
    \end{defn}

    \begin{defn}
    Given an undirected graph G, the $

\textit{spectral radius}$  $\rho(G) $ of G is the spectral radius of the adjacency

matrix of G.
    \end{defn}

    We introduce a notation of submatrix, which is

taken from some columns and some rows of a matrix.
    \begin{defn}
        For a

matrix $C=(c_{ij})$ and subsets $\alpha$, $\beta$ of row indices and column

indices of 
        $C$ respectively,  We use $C[\alpha|\beta]$ to denote the

submatrix of $C$ with size
         $ |\alpha| \times |\beta| $ that has entries

$c_{ij}$ for $i\in \alpha$ and $j\in\beta$,
    \end{defn}

We introduce two

matrices $P$ and $Q$ in the following theorem, where $P$ is a permutation matrix

which is multiplied to the left side, and $Q$ is sum of elementary matrix and

certain binary matrix. In which $P$ generalize row permutation on cases of $C$

matrix,and $Q$ is the transform from $C'$ to C', which is the first n-1 columns

and sum of certain columns. We aim to find C' such that $C'$ majors $C$,i.e. $C

\leq C'$

The following theorem is from [].\cite{content}

    \begin

{thm}\label{pre_thm}
        Let $C=(c_{ij})$, $C'=(c'_{ij})$, $P$ and $Q$ be  $n

\times n$ matrices.
        Assume that
        \begin{enumerate}

\item[(i)]    $PCQ\leq PC'Q$;\label{Q1}
            \item[(ii)]  there exist a

nonnegative column vector $u=(u_1, u_2, \ldots, u_n)^T$  and a scalar $\lambda'\in

\mathbb{R}$ such that $\lambda'$ is an eigenvalue of $C'$ with associated

eigenvector $Qu$;
            \item[(iii)] there exist a nonnegative row vector

$v^T=(v_1, v_2, \ldots, v_n)$  and a scalar $\lambda\in \mathbb{R}$

such that $\lambda$ is an eigenvalue of $C$ with associated  left eigenvector

$v^TP$; and
            \item[(iv)] $v^TPQu>0.$
            \end{enumerate}

     Then $\lambda\leq \lambda'$.
                Moreover, $\lambda=\lambda'$

         if and only if
                \begin{equation}

\label{e3}
            (PC'Q)_{ij}=(PCQ)_{ij}\qquad \hbox{for~}1\leq i, j\leq n

\hbox{~with~} v_i\ne 0 \hbox{~and~} u_j\ne 0.
        \end{equation}
    \end

{thm}%

    % { Proof}
            Multiplying the nonnegative vector $u$ in

(ii) to the right of both terms of  (i),
        \begin{equation}\label{e1}

     PCQu\leq PC'Qu=\lambda'PQu.
        \end{equation}
        Multiplying the

nonnegative left eigenvector $v^T$ of $C$ for $\lambda$ in assumption (iii) to the

left of all terms  in (\ref{e1}), we have
        \begin{equation}\label{e2}

      \lambda v^TPQu=v^TPCQu\leq v^TPC'Qu=\lambda' v^TPQu.
        \end{equation}

       Now delete the positive term $v^TPQu$ by assumption (iv) to obtain $

\lambda\leq \lambda'$ and finish the proof of the first part.

    { Proof

(Continue)}
        Assume that $\lambda=\lambda'$, so the inequality in (\ref

{e2}) is an equality.  Especially $(PCQu)_i=(PC'Qu)_i$ for any $i$ with $v_i

\not=0.$ Hence, $(PCQ)_{ij}=(PC'Q)_{ij}$ for any $i$ with $v_i\not=0$ and any $j$

with $u_j\not=0.$ 
         Conversely, (\ref{e3}) implies $$v^TPCQu=\sum_{i,j}

v_i(PCQ)_{ij}u_j=\sum_{i,j} v_i(PC'Q)_{ij}u_j=v^TPC'Qu,$$ so
            $

\lambda=\lambda'$ by (\ref{e2}).

\section{Our Method}
We use [n-1] as notation of the set of elements from one to n-1, which is {1,2,$...$,n}.
Throughout fix $k\in [n-1]$.Let $E_{kn}$ denote the $n\times n$ binary matrix with a unique $1$ appearing in the position $k,n$ of $E_{kn}$. We will apply the previous theorem with $P=I$ and

\begin{equation}
Q=I+E_{kn}=\begin{pmatrix} \label{Q1}
1 &  & & &  & 0 \\
 & 1 &  &      &  &  \\
 &  & \ddots & &  & 1 \\
 &  &        & &  &  \\
  &  & & & 1 &  \\
0 &  & & &  & 1 \\
\end{pmatrix}.
\end{equation}

\begin{defn}[$k$-rooted vector]
~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
\end{defn}
\bigskip

@@

\begin{lem}[vector rooted lemma]\label{v_rooted}
If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
\begin{enumerate}
\item[(i)] $v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
\item[(ii)] $u_k>0$ if and only if $v'_k>v'_n$.
\end{enumerate}
\qed
\end{lem}

\begin{thm}[Our first result]\label{thm_main}
    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}
\item[(i)]   $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
\item[(ii)] there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
\item[(iii)] there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
\item[(iv)] $v^Tv'>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{enumerate}
    \item[(a)]    $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
    \item[(b)]  $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $with $v_i\ne 0 $;
    \item[(c)]   $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$ 
\end{enumerate} \qed
\end{thm}
%

@@

    We are interested in the matrices $C'$ that have $k$-rooted eigenvectors.
    Motivated by the condition (i) of theorem 2.3, we provide the following two definitions.

    \begin{defn}[(k,n)-sum]
        For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$, where $k\leq n-1$.
    \end{defn}

    Note that the last column of $C'Q$ is the $(k, n)$-{\it sum} vector of $C'$

@@

\begin{Proof}

The assumptions are necessary that $PCQ \leq PC'Q$, and C' is k-rooted, by (\ref{v_rooted}),
 For certain d, if C'+dI is k-rooted, then it has a k-rooted eigenvector with its spectral
  radius $\lambda + d$. C' would share the same eigenvector with C'+dI and has eigenvalue
   $\lambda$. So C'+dI and C+dI meet the conditions of (\ref{l_diag}), and we can show that
    $\rho(C' + dI) \geq \rho(C +dI)$ and then $\rho(C') \geq \rho(C)$  \qed    
\end{proof}

\subsection{Example}
    For the following $4\times 4$ matrix
    $$C=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 0 & 1\\
    1 & 1 & 0 & 1\\
    1 & 1 & 1 & 0
    \end{pmatrix},$$
    we choose
    $$C'=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 1 &  0\\
    1 & 1 & 0 & 1\\
    1 & 1 & 1 & 0
    \end{pmatrix}.$$
    Check the conditions $C[[n]|[n-1]]  \leq C'[[n]|[n-1]] $ \ref{thm_main},
    Then
    $\rho(C)\leq \rho(C')$ by previous theorem.

\subsection{Counterexample}
    For the following two $4\times 4$ matrices
    $$C=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 0 & 1\\
    1 & 1 & 0 & 0\\
    1 & 1 & 1 & 0
    \end{pmatrix},\quad C'=\begin{pmatrix}
    0 & 0 & 1 & 1\\
    1 & 0 & 1 &  0\\
    1 & 1 & 0 & 0\\
    1 & 1 & 1 & 0
    \end{pmatrix},$$ 
    specify $n$=4, $k$=3 in $Q = I +E_{kn} = I + E_{34}$  
$$CQ=\begin{pmatrix}
0 & 0 & 1 & 2\\
1 & 0 & 0 & 1\\
1 & 1 & 0 & 0\\
1 & 1 & 1 & 1
\end{pmatrix},\quad C'Q=\begin{pmatrix}
0 & 0 & 1 & 2\\
1 & 0 & 1 & 1\\
1 & 1 & 0 & 0\\
1 & 1 & 1 & 1
\end{pmatrix},$$

    we have $CQ\leq C'Q$, but 
    $\rho(C)=2.234\not\leq 2.148= \rho(C')$. 
    This is because $c'_{33}+c'_{34}\not\geq c'_{43}+c'_{44}$.

### 2020-11-04 spectral radius of matrix new method/thesis/our_result.tex
proof 1.8 line cut
1104 temp saved

\documentclass[12pt]{report}%{article}

@@

@@

\begin{defn}\label{v_rooted}
 ~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
\end{defn}
\bigskip

@@

\begin{lem}
If ~$u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
\begin{enumerate}
\item[(i)] $v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
\item[(ii)] $u_k>0$ if and only if $v'_k>v'_n$.
\end{enumerate}
\qed
\end{lem}

\begin{thm} \label{thm_main}
    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}
\item[(i)]   $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
\item[(ii)] there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
\item[(iii)] there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
\item[(iv)] $v^Tv'>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{enumerate}
\item[(a)]    $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
\item[(b)]  $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $with $v_i\ne 0 $;
\item[(c)]   $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$ 
\end{enumerate} \qed

\end{thm}

\begin{proof}
The proof is based on Theorem 1.7 with $P = I$ and $Q = I + E_{kn} \text{ in } (\ref{Q1} )  $. The assumption (i) $PCQ\leq PC'Q$ of Theorem 1.7 holds by the condition (i) of this theorem. Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition (ii) and Lemma 2.2(i). Hence the assumption (ii) of Theorem 1.7 holds. The assumptions (iii) and (iv) of Theorem 1.7 clearly hold by conditions (iii),(iv) of this theorem since $P = I$ and $v'= Qu$  Hence $\lambda \leq \lambda' $ by the conclusion of Theorem 1.7. Moreover $\lambda = \lambda'$ if and only if \ref{pre0} holds, and this is equivalent to conditions (a),(b),(c) of this theorem. 
\end{proof}

@@

\begin{defn}
For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$.
\end{defn}

@@

(ii)
By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted.
Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
$Q^{-1} C' Q u  = Q^{-1} \rho(C') Qu  =\rho(C')u$
$C'Qu=\rho(C')Qu$.

@@

The assumptions are necessary that $PCQ \leq PC'Q$, and C' is $k$-rooted,based on (\ref{lma_m_rooted}) ; by \ref{l_diag}, For certain d, if $C'+dI$ is $k$-rooted, then it has a $k$-rooted eigenvector with its spectral radius $\lambda + d$. C' would share the same eigenvector with $C'+dI$ and has eigenvalue $\lambda$. So $C'+dI$ and $C+dI$ meet the conditions of \ref{thm_main}, and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and then $\rho(C') \geq \rho(C)$  \qed

>>>>

\documentclass[12pt]{report}

@@

\usepackage{comment}

@@

\begin{defn}[$k$-rooted vector]%\label{k_rooted}
 ~A column vector $v'=(v'_1,v'_2,\ldots,v'_n)^T$ is called {\it $k$-rooted}  if $v'_{j} \geq 0$ for $1 \leq  j \leq n$ and $v'_k\geq v'_n.$
\end{defn}
\bigskip

@@

\begin{lem}
If $u=(u_1, u_2, \ldots, u_n)^T$ and $v'=(v'_1, v'_2, \ldots, v'_n):=Qu=(u_1,\ldots, u_{k-1},u_k+u_n, u_{k+1}, \ldots,  u_n)^T$, then
\begin{enumerate}
\item[(i)] $v'$ is $k$-rooted  if and only if  $u$ is nonnegative;
\item[(ii)] $u_k>0$ if and only if $v'_k>v'_n$.
\end{enumerate}
\qed
\end{lem}

\begin{thm} \label{thm_main}
    Let $C=(c_{ij})$, $C'=(c'_{ij})$ be  $n\times n$ matrices.
Assume that
\begin{enumerate}
\item[(i)]   $C[[n]|[n-1]]\leq C'[[n]|[n-1]]$ and $c_{ik}+c_{in}\leq c'_{ik}+c'_{in}$ for all $1\leq i\leq n$;
\item[(ii)] there exists a $k$-rooted vector $v'=(v'_1, v'_2, \ldots, v'_n)^T$ and a scalar $\lambda'\in \mathbb{R}$
such that $\lambda'$ is an eigenvalue of $C'$ with associated eigenvector $v'$;
\item[(iii)] there exists a nonnegative vector $v^T=(v_1, v_2, \ldots, v_n)$ and a scalar $\lambda\in \mathbb{R}$ such that $\lambda$ is an eigenvalue of $C$ with associated left eigenvector $v^T$;
\item[(iv)] $v^Tv'>0.$
\end{enumerate}
 Then $\lambda\leq \lambda'$.
Moreover, $\lambda=\lambda'$
if and only if
\begin{enumerate}
\item[(a)]    $c_{ik}+c_{in}=c'_{ik}+c'_{in} \qquad$  for $1\leq i\leq n$ with $v_i\not=0$ and $v'_n\not=0;$
\item[(b)]  $c'_{ij}=c_{ij}\qquad $for $1\leq i\leq n,~1\leq j\leq n-1, j \neq k $with $v_i\ne 0 $;
\item[(c)]   $c'_{ik}=c_{ik} \qquad $  for $1\leq i \leq n$ and $ v'_{k}>v'_n$ 
\end{enumerate} \qed
\end{thm}

\begin{proof}
The proof is based on Theorem 1.7 with $P = I$ and $Q = I + E_{kn} \text{ in } (\ref{Q1} )$. 
The assumption (i) $PCQ\leq PC'Q$ of Theorem 1.7 holds by the condition (i) of this theorem. 
Let $u = Q^{-1}v'$. Then u is nonnegative and $C'Qu = \lambda' Qu$ by the condition (ii) and
 Lemma 2.2(i). Hence the assumption (ii) of Theorem 1.7 holds. The assumptions (iii) and (iv)
  of Theorem 1.7 clearly hold by conditions (iii),(iv) of this theorem since $P = I$ and
   $v'= Qu$  Hence $\lambda \leq \lambda' $ by the conclusion of Theorem 1.7. Moreover
    $\lambda = \lambda'$ if and only if \ref{pre0} holds, and this is equivalent to
     conditions (a),(b),(c) of this theorem. 
\end{proof}

@@

\begin{defn}[(k,n)-sum]
For an $n \times n$ matrix $C'=(c'_{ij})$, the $(k, n)$-{\it sum} vector of $C'$ is the vector of the sum of the $k$-th and  $n$-th columns of $C'$.
\end{defn}

@@

(ii)
By Lemma~\ref{v_rooted} $v'=Qu$ is $k$-rooted.
Since $Q^{-1}C'Qu=\rho(C')u$ by the assumption, we have
$Q^{-1} C' Q u  = Q^{-1} \rho(C') Qu  =\rho(C')u$  \\
$C'Qu=\rho(C')Qu$.

@@

The assumptions are necessary that $PCQ \leq PC'Q$, and C' is $k$-rooted,based on
 (\ref{lma_m_rooted}) ; by \ref{l_diag}, For certain d, if $C'+dI$ is $k$-rooted, then it has
  a $k$-rooted eigenvector with its spectral radius $\lambda + d$. C' would share the same
   eigenvector with $C'+dI$ and has eigenvalue $\lambda$. So $C'+dI$ and $C+dI$ meet the
    conditions of \ref{thm_main}, and we can show that $\rho(C' + dI) \geq \rho(C +dI)$ and
     then $\rho(C') \geq \rho(C)$  \qed
\end{proof}
